RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-05-07 discussion.tex
Fixed a bit the conclusion

The process of constructing a goal model involves discussions between a requirements engineer and a group of stakeholders. While it is possible to capture part of this discussion process in a goal model, for instance by specifying alternative solutions for a goal, not all of the arguments can be found back in the resulting model. This makes it not only more difficult to understand the model, but other stakeholders may end up having similar discussions throughout the design and development phase as well. Furthermore, the disconnect between goal models and their underlying beliefs and opinions may lead to a poor understanding of the problem and solution domain.

@@

Our list of argument schemes and critical questions in Table~\ref{table:argument-schemes} was constructed by performing an extensive case study in which we analyzed 153 pages of transcripts of discussions among designers of a traffic simulator information system. In this way, we ensure that he argumentation techniques capture the actual discussions of the stakeholders or designers in the early requirements engineering phase (\textbf{requirement 1}).

The metamodel of the RationalGRL framework in Figure~\ref{fig:metamodel} clearly specifies the formal traceability links elements of the GRL goal model and the underlying arguments. (\textbf{requirement 2}). In addition to this metamodel, we provide formal semantics for RationalGRL by formalizing the GRL language in propositional logic and rendering arguments about a GRL model as a formal argumentation framework~\cite{Dung1995}. We, then, formally capture the link between argumentation and goal modeling as a set of algorithms for applying argument schemes and critical questions about goal models. These formal traceability links allow us to compute the effect of the arguments and counterarguments proposed in a discussion on a GRL model (\textbf{requirement 3}). In other words, we can determine whether the elements of a GRL model are acceptable given potentially contradictory opinions of stakeholders. Thus, we add a new formal evaluation technique for goal models that allows us to assess the \emph{acceptability} of elements of a goal model (in addition to their \emph{satisfiability}~\cite{Amyot:2010:EGM:1841349.1841356}).

>>>>

The process of constructing a goal model involves discussions between requirements engineers and a group of stakeholders. While it is possible to capture part of this discussion process in a goal model, for instance by specifying alternative solutions for a goal, not all of the arguments can be found back in the resulting model. This makes it not only more difficult to understand the model, but other stakeholders may end up having similar discussions throughout the design and development phase as well. Furthermore, the disconnect between goal models and their underlying beliefs and opinions may lead to a poor understanding of the problem and solution domain.

@@

Our list of argument schemes and critical questions in Table~\ref{table:argument-schemes} was constructed by performing an extensive case study in which we analyzed 153 pages of transcripts of discussions among designers of a traffic simulator information system. In this way, we ensure that the argumentation techniques capture the actual discussions of the stakeholders or designers in the early requirements engineering phase (\textbf{requirement 1}).

The metamodel of the RationalGRL framework in Figure~\ref{fig:metamodel} clearly specifies the formal traceability links elements of GRL goal model and the underlying arguments. (\textbf{requirement 2}). In addition to this metamodel, we provide formal semantics for RationalGRL by formalizing the GRL language in propositional logic and rendering arguments about a GRL model as a formal argumentation framework~\cite{Dung1995}. We, then, formally capture the link between argumentation and goal modeling as a set of algorithms for applying argument schemes and critical questions about goal models. These formal traceability links allow us to compute the effect of the arguments and counterarguments proposed in a discussion on a GRL model (\textbf{requirement 3}). In other words, we can determine whether the elements of a GRL model are acceptable given potentially contradictory opinions of stakeholders. Thus, we add a new formal evaluation technique for goal models that allows us to assess the \emph{acceptability} of elements of a goal model (in addition to their \emph{satisfiability}~\cite{Amyot:2010:EGM:1841349.1841356}).
